---
title: "About the project"
author: "Mihir Bhaskar"
date: "16/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(tidyverse, sp, leaflet, rgdal, maptools, tmap, stringr)
boundaries <- readOGR("D:/Dropbox/Mayur Vihar Project/Listing Survey/Data/Raw/Blocks for listing.kml",
                      require_geomType='wkbPolygon')


```

This website showcases work on a small scale community development project in New Delhi. We have been working with 'jhuggis' (slums) near the banks of the Yamuna River in Mayur Vihar Phase-I. 


```{r boundary}

# Prepping and merging on survey data

#boundaries@data <- left_join(boundaries@data, survey, by = 'block_name') 

leaflet() %>% addTiles() %>% addPolygons(data = boundaries)

```

By virtue of the location

-	Delhi government says development can’t happen because it’s 300m from the banks of the Yamuna 
-	However, the issue is Delhi Development Authority (DDA) comes and demolishes constructions and evicts people without giving fair dues https://www.hindustantimes.com/cities/dda-demolishes-hundreds-of-hutments-on-yamuna-floodplain/story-x105Sl8yPf2tLgUFM0XLRK.html

- Some photos of the area; mainly engaged in agriculture, living in huts, some as labourers. Migrant community


It is sometimes hard to believe that such a community exists in the heart of the nation's capital 

