---
title: "About the project"
author: "Mihir Bhaskar"
date: "16/08/2020"
output: html_document
weight: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(tidyverse, sp, leaflet, rgdal, maptools, tmap, stringr)
boundaries <- readOGR("D:/Dropbox/Mayur Vihar Project/Listing Survey/Data/Raw/Blocks for listing.kml",
                      require_geomType='wkbPolygon')


```

This website showcases work on a small scale community development project in New Delhi. Focusing on the 'jhuggis' (slums) near the banks of the Yamuna River in Mayur Vihar Phase-I, we have been working to:

1. **Fulfill pressing, short-term needs through targeted campaigns.** The two campaigns completed so far include free distribution of tarpaulins as storm relief, and free distribution of mosquito nets in anticipation of the monsoons. You can read more about these by clicking on the respective tabs.

2. **Develop a detailed understanding of the community to help plan interventions for longer-term and sustained improvements in quality of life.** You can read more about our efforts on this front by visiting the 'About the community' page.

You can see the specific areas we are focusing on highlighted in blue on the map below, and get a rough sense of how things look 'on the ground' through the pictures. We sometimes still find it hard to believe that such a community exists in the heart of the nation's capital! 


```{r boundary}

# Prepping and merging on survey data

#boundaries@data <- left_join(boundaries@data, survey, by = 'block_name') 

leaflet() %>% addTiles() %>% addPolygons(data = boundaries)

```
